Prospects of detecting gamma-ray emission from galaxy clusters: cosmic rays and dark matter annihilations

### 2011-05-13 paper.tex
corrections to text

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v11.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv11.0.1deg.SubMass.noMW.woGal.eps}
\caption{\it Comparing the flux from different inverse Compton
  upscattered radiation fields. We show the differential inverse
  Compton emission induced by leptophilic DM in the left panel and by
  the $\Kp$ benchmark model in the right panel. The contribution from
  each individual radiation field from top line to bottom line; CMB
  (green dashed-triple-dotted), dust (purple dashed), stars (blue
  dashed-dotted). The sum of the three components are shown with the
  orange solid line.  The red solid line show the CR induced
  gamma-ray flux. The black arrow shows the differential upper limit
  from Fermi \protect \cite{2010ApJ...717L..71A} indicating that the model
  assumptions such as Sommerfeld and/or substructure boost are in
  conflict with the upper limit. All fluxes are calculated for the
  Fornax cluster within $\rvir$ using a point spread function of
  $0.1\deg$. For this cluster, the boost from Sommerfeld is about 130
  and the enhancement due to substructures from IC upscattered CMB and
  SD photons is 570 and 20, respectively.}
 \label{fig:IR_comp}
\end{minipage}
\end{figure*}

>>>>

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v11.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv11.0.1deg.SubMass.noMW.woGal.eps}
\caption{\it Comparing the flux from different inverse Compton
  upscattered radiation fields. We show the differential inverse
  Compton emission induced by leptophilic DM in the left panel and by
  the $\Kp$ benchmark model in the right panel. The contribution from
  each individual radiation field from top line to bottom line; CMB
  (green dashed-triple-dotted), dust (purple dashed), stars (blue
  dashed-dotted). The sum of the three components are shown with the
  orange solid line.  The red solid line show the CR induced gamma-ray
  flux. The black arrow shows the differential upper limit from Fermi
  \protect \cite{2010ApJ...717L..71A} indicating that the model
  assumptions such as Sommerfeld and/or substructure boost are in
  conflict with the upper limit. We also show projected CTA point
  source sensitivities ($5\sigma$, 50h).  All fluxes are calculated
  for the Fornax cluster within $\rvir$ using a point spread function
  of $0.1\deg$. For this cluster, the boost from Sommerfeld is about
  130 and the enhancement due to substructures from IC upscattered CMB
  and SD photons is 570 and 20, respectively.}
 \label{fig:IR_comp}
\end{minipage}
\end{figure*}
